### 2023-03-10 paper.tex
Add references and todo

The models this paper discusses very closely follow the initial architecture
presented in the paper originally proposing the transformer 
\cite{vaswani_attention_2017}. Most of the differences between 
the models come down to training.

TODO: talk about masking the attention layers somewhere, was talked about in
the t5 paper

>>>>

The models this paper discusses closely follow the initial architecture
presented in the paper originally proposing the transformer 
\cite{vaswani_attention_2017}. Most of the differences between 
the models come down to training, attention layer masking and the encoder-decoder layers
\cite{raffel_exploring_2020}.

TODO: talk about masking the attention layers somewhere, was talked about in
the t5 paper
TODO: talk about masking, t5 paper lists this as the biggest differentiating factor
between models. the t5 paper is also good source for general comparison between different
architectures and approaches
(the above two are the same)
